Functional Data Analysis (FDA) is a branch of Statistics devoted
to the study of random quantities that depend on a continuous parameter,
such as time series or curves in space.
In FDA the data instances can be viewed as random functions
sampled from an underlying stochastic process.

In this work we consider three different tasks in FDA:
the use of interpolation techniques to estimate the values
of the functions at unobserved points,
the registration of these type of data,
and the solution of classification and regression problems in which
the instances are characterized by functional attributes.
In particular, in this project the \textit{scikit-fda} package
for FDA in Python has been extended
with functionality in these areas.

Generally, the data instances considered in FDA consist of a
collection of observations at a discrete values of the parameter
on which they depend (e.g. time or space).
For some applications it is convenient, and in some cases
necessary, to estimate the value of these functions
at unobserved points.
This can be achieved through the use of interpolation
from the available measurements.

In some applications, the functions observed
have similar shapes, but exhibit variability whose
origin can be traced to distortions in the scale
of the continuous parameter on which the data depend.
Registration consists in characterizing
this variability and eliminating it from the sample considered.

In this work we also address classification and regression problems
with data that are characterized by functions.
Specifically, we design nearest neighbors estimators
based on the notion of closeness among samples.

Specifically, in this work have been implemented interpolation methods based on
splines, as well as functionalities for data registration using shift
registration and landmark registration, along with elastic registration,
method based on the Fisher-Rao metric. In addition, models based on nearest
neighbors have been included to perform regression, for scalar and functional
response, and classification.
